Manifold Destiny - or how to rig an election

### 2024-01-02 index.qmd
haplo

### Install and load packages
```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
library(magrittr)
md <- ManifoldDestinyWASMD::metad
library(dplyr)
library(combinat)
library(htmltools)
library(ggplot2)
library(broom)
library(combinat)
```

@@

>>>>

### Install and load packages
```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("AlgebraicHaploPackage","cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
library(magrittr)
md <- ManifoldDestinyWASMD::metad
library(dplyr)
library(combinat)
library(htmltools)
library(ggplot2)
library(broom)
library(tidyr)
library(combinat)
library(AlgebraicHaploPackage)
```

@@

#### Normal
```{webr-r}
app_n_rep <- selreport(app_bal,md$app0)
app_n_out <- seloutput(app_n_rep)
app_n_sim <- SimVoterdatabase(app_bal)
```

#### Functions
```{webr-r}
2+2
```

#### Rig 1: Normal
```{webr-r}
app_ex1_cou <- Countinggraphs(app_bal)
print(app_ex1_cou$polyc[[1]][[1]])
app_ex1_cou$sortpre()
app_ex1_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
app_ex1_cou$setres(0.23,0)
app_ex1_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),TRUE,wn=c(0,0))
app_ex1_out <- seloutput(selreport(app_ex1_cou$rdfc,md$app0))
app_ex1_sim <- SimVoterdatabase(app_ex1_cou$rdfc)
```

#### Rig 2: Hybdrid
```{webr-r}
app_ex2_cou <- Countinggraphs(app_bal)
pri_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
print(app_ex2_cou$polyc[[1]][[1]])
app_ex2_cou$sortpre()
app_ex2_cou$mansys(sygen=list(frm=2,pre=c("alpha","g","h"),end=c("Gamma","Omega"),FALSE,me=c(plnr=1,rot=0)))
app_ex2_cou$setres(0.23,0)
app_ex2_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
app_ex2_out <- seloutput(selreport(app_ex2_cou$rdfc,md$app0))
app_ex2_sim <- SimVoterdatabase(app_ex2_cou$rdfc)
```

#### Rig 3: Opposition
```{webr-r}
app_ex3_cou <- Countinggraphs(app_bal)
pri_int_ex3 <- app_ex3_cou$polyc[[1]][[1]]
app_ex3_cou$sortpre()
app_ex3_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
app_ex3_cou$setres(0.23,0)
app_ex3_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
app_ex3_out <- seloutput(selreport(app_ex3_cou$rdfc,md$app0))
app_ex3_sim <- SimVoterdatabase(app_ex3_cou$rdfc)
```
